---
output:
  md_document:
    variant: gfm
---

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/maddison)](http://cran.r-project.org/package=maddison)
[![](http://cranlogs.r-pkg.org/badges/grand-total/maddison)](http://cran.r-project.org/web/packages/maddison)


## Maddison Project Database

This package contains the [Maddison Project Database](http://www.ggdc.net/maddison), which contains estimates of GDP per capita for all countries in the world between AD 1 and 2016, in a format amenable to analysis in R.

The database was last updated in 2018.

As per instructions on the Maddison Project website, please site the data as follows:

> __Attribution requirement__ - When using these data (for whatever purpose), please make the following reference:
> - Maddison Project Database, version 2018. Bolt, Jutta, Robert Inklaar, Herman de Jong and Jan Luiten van Zanden (2018), “Rebasing ‘Maddison’: new income comparisons and the shape of long-run economic development”, [Maddison Project Working paper 10](https://www.rug.nl/ggdc/historicaldevelopment/maddison/research)
> - For the references to the original research on individual countries, see Appendix A of Bolt et al. (2018).

## Example use

```{r, echo = FALSE}
knitr::opts_chunk$set(fig.path = "man/figures/README-")
```

```{r, eval = FALSE}
# to install from Github
install.packages("remotes")
remotes::install_github("expersso/maddison")
```

```{r}
library(maddison)
str(maddison)
head(maddison)
```

```{r line_plot, fig.width = 6, fig.height = 3, fig.align = 'center', warning = FALSE, message = FALSE}
library(ggplot2)
library(dplyr)
library(scales)

# Data frame with annotations
df_annotate <- data.frame(
  xmin = c(1914, 1939),
  xmax = c(1918, 1945),
  ymin = c(900, 900), ymax = c(3e4, 3e4),
  label = c("WW1", "WW2"))

maddison %>%
  filter(iso2c %in% c("DE", "FR", "IT", "UK", "US")) %>%
  filter(year >= 1800) %>%
  ggplot() +
  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            data = df_annotate, fill = "grey50", alpha = 0.25) +
  geom_text(aes(label = label, x = xmin, y = ymax), data = df_annotate, 
            vjust = 0, hjust = 0, nudge_y = 0.02, size = 3) +
  geom_line(aes(x = year, y = rgdpnapc, color = country)) +
  scale_y_log10(labels = comma, breaks = pretty_breaks(8)) +
  theme_bw(8) +
  labs(x = NULL, y = "GDP per capita (2011 US$)\n", color = NULL,
       title = "GDP per capita (1800-2016)")
```

## Disclaimer

This package is not affiliated with, nor endorsed by, the Maddison Project. I
aim to update it whenever the database is updated. If you ever see that it
is out-of-date, don't hesitate to send a pull request and/or remind me to update
it.
