---
output:
  md_document:
    variant: markdown_github
---

## Maddison Project Dataset

This package contains the [Maddison Project
Dataset](http://www.ggdc.net/maddison/maddison-project/data.htm) with estimates
of GDP per capita for all countries in the world between AD 1 and 2010 in a
format amenable to analysis in R.

The database was last updated in January 2013.

As per instructions on the Maddison Project website, please site the data as
follows:

| Purpose | Citation |
|--------------|---------------|
| When using the data | The Maddison-Project, <http://www.ggdc.net/maddison/maddison-project/home.htm>, 2013 version.  |
| When refering to underlying methodology and main results | Bolt, J. and J. L. van Zanden (2014). The Maddison Project: collaborative research on historical national accounts. The Economic History Review, 67 (3): 627-651. When using individual country data |
| When using individual country data | See country-source references in the appendix of Bolt and van Zanden (2014). |

## Example use

```{r, echo = FALSE}
knitr::opts_chunk$set(fig.path = "")
```


```{r, eval = FALSE}
# To install from Github
library(devtools)
install_github("expersso/maddison")
```

```{r}
library(maddison)
str(maddison)
head(maddison)
```

```{r plot, fig.width = 6, fig.height = 3, fig.align='center', warning=FALSE, message=FALSE}

library(ggplot2)
library(dplyr)
library(scales)

# Data frame with annotations
df_annotate <- data.frame(
  xmin = as.Date(c("1914-01-01", "1939-01-01")),
  xmax = as.Date(c("1918-01-01", "1945-01-01")),
  ymin = c(900, 900), ymax = c(3e4, 3e4),
  label = c("WWI", "WW2"))

maddison %>%
  filter(iso2c %in% c("DE", "FR", "IT", "UK", "US")) %>%
  filter(year >= as.Date("1800-01-01")) %>%
  ggplot() +
  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            data = df_annotate, fill = "grey50", alpha = 0.25) +
  geom_text(aes(label = label, x = xmin, y = ymax), data = df_annotate, 
            vjust = 0, hjust = 0, nudge_y = 0.02, size = 3) +
  geom_line(aes(x = year, y = gdp_pc, color = country)) +
  scale_y_log10(labels = comma, breaks = pretty_breaks(8)) +
  coord_cartesian(ylim = c(900, 35000)) +
  theme_bw(8) +
  labs(x = NULL, y = "GDP per capita (1990 Int. GK$)\n", color = NULL,
       title = "GDP per capita (1800-2010)")
```

## Disclaimer

This package is not affiliated with, nor endorsed by, the Maddison Project. I
aim to update it whenever the database is updated. If you ever see that it
is out-of-date, don't hesitate to send a pull request and/or remind me to update
it.
