---
title: "Maddison Project Dataset"
author: "Eric Persson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

This package contains the [Maddison Project
Dataset](http://www.ggdc.net/maddison/maddison-project/data.htm) with estimates
of GDP per capita for all countries in the world between AD 1 and 2010 in a
format amenable to analysis in R.

The database was last updated in January 2013.

As per instructions on the Maddison Project website, please site the data as
follows:

| Purpose | Citation |
|--------------|---------------|
| When using the data | The Maddison-Project, <http://www.ggdc.net/maddison/maddison-project/home.htm>, 2013 version.  |
| When refering to underlying methodology and main results | Bolt, J. and J. L. van Zanden (2014). The Maddison Project: collaborative research on historical national accounts. The Economic History Review, 67 (3): 627-651. When using individual country data |
| When using individual country data | See country-source references in the appendix of Bolt and van Zanden (2014). |

## Example use

```{r, warning=FALSE, message=FALSE}
library(maddison)
library(ggplot2)

str(maddison)
head(maddison)
```

```{r, fig.width = 6, fig.height = 4, warning=FALSE, message=FALSE}
df <- subset(maddison, 
             year >= as.Date("1800-01-01") &
             iso2c %in% c("DE", "FR", "IT", "UK", "US"))

ggplot(df, aes(x = year, y = gdp_pc, color = country)) +
  geom_line() +
  scale_y_log10() +
  theme_bw() +
  labs(x = NULL, y = "GDP per capita (1990 Int. GK dollars)\n", color = NULL,
       title = "GDP per capita (1800-2010)")
```

## Disclaimer

This package is not affiliated with, nor endorsed by, the Maddison Project. I
aim to update it whenever the database is updated. If you ever see that it
is out-of-date, don't hesitate to send a pull request and/or remind me to update
it.
